High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-04-06 notebooks/mnist.qmd
bloody jupyter seriously

```{julia}
epochs = 100
clf = NeuralNetworkClassifier(
    builder=MLJFlux.MLP(hidden=(32,), σ=relu), 
    epochs=epochs,
    batch_size=Int(round(n_obs/10))
)
conf_model = conformal_model(clf; method=:simple_inductive, coverage=.99)
mach = machine(conf_model, X, labels)
fit!(mach)
```

@@

```{julia}
# Set up search:
factual_label = 9
x = reshape(counterfactual_data.X[:,rand(findall(predict_label(M, counterfactual_data).==factual_label))],input_dim,1)
target = 4
factual = predict_label(M, counterfactual_data, x)[1]
γ = 0.9
T = 100

@@

# Generate counterfactual using CCE generator:
generator = CCEGenerator(
    λ=[0.0,10.0], 
    temp=0.01, 
    # opt=CounterfactualExplanations.Generators.JSMADescent(η=5.0),
)
ce_conformal = generate_counterfactual(
    x, target, dt_reduced, M, generator; 
    decision_threshold=γ, max_iter=T,
    initialization=:identity,
    converge_when=:generator_conditions,
)
```

```{julia}
p1 = Plots.plot(
    convert2image(MNIST, reshape(x,28,28)),
    axis=nothing, 
    size=(img_height, img_height),
    title="Factual"
)
plts = [p1]

>>>>

```{julia}
epochs = 100
clf = NeuralNetworkClassifier(
    builder=MLJFlux.MLP(hidden=(32,), σ=relu), 
    epochs=epochs,
    batch_size=Int(round(n_obs/10))
)
conf_model = conformal_model(clf; method=:adaptive_inductive, coverage=.99)
mach = machine(conf_model, X, labels)
fit!(mach)
```

@@

```{julia}
# Set up search:
factual_label = 8
x = reshape(counterfactual_data.X[:,rand(findall(predict_label(M, counterfactual_data).==factual_label))],input_dim,1)
target = 3
factual = predict_label(M, counterfactual_data, x)[1]
γ = 0.9
T = 100

@@

# Generate counterfactual using CCE generator:
generator = CCEGenerator(
    λ=[0.0,100.0], 
    temp=0.01, 
    # opt=CounterfactualExplanations.Generators.JSMADescent(η=5.0),
)
ce_conformal = generate_counterfactual(
    x, target, dt_reduced, M, generator; 
    decision_threshold=γ, max_iter=T,
    initialization=:identity,
    converge_when=:generator_conditions,
)

# Plot:
p1 = Plots.plot(
    convert2image(MNIST, reshape(x,28,28)),
    axis=nothing, 
    size=(img_height, img_height),
    title="Factual"
)
plts = [p1]
